Interest Flooding Attacks and countermeasures in Named Data Networking

### 2013-01-14 05-evaluation.tex
Small spacing changes (there was text overlapping on figures)
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@916 df1a90cd-247b-4364-bdaf-287a704eb499

\begin{figure}[]
  \centering
  \vspace{-.2cm}\hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
  \vspace{-.5cm}\caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
  \label{fig:small-scale attack progress}
\vspace{-.5cm}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
  \vspace{-.6cm}\caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
  \label{fig:small-scale-topo boxplot}
\end{figure}

@@

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
 \vspace{-.7cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}

>>>>

\begin{figure}[]
  \centering
  \hspace{-0.8cm}\includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw}
  \vspace{-.3cm}
  \caption{Interest satisfaction ratio as a function of time for binary-tree topology with 7 attackers and 9 legitimate users}
  \label{fig:small-scale attack progress}
  \vspace{-.4cm}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.8]{paper-topo-tree/tree-good-0-producer-gw-avg-1-min}
  \vspace{-.3cm}
  \caption{Average Interest satisfaction ratios for the first minute of the experiment as a function of increasing attackers in the network}\vspace{-.1cm}
  \label{fig:small-scale-topo boxplot}
\end{figure}

@@

\begin{figure}[tbh]
 \centering
 \includegraphics[scale=0.8]{paper-topo-7018-gw/7018-r0-good-0-producer-gw}
 \vspace{-.3cm}\caption{Satisfaction ratio dynamics during the attack for large-scale topology with 40\% attackers)}\vspace{-.4cm}
 % producer on a gateway node
 \label{fig:large-scale}
\end{figure}
